\input{preamble}

% OK, start here.
%
\input{chapter_modifications.tex}
\begin{document}

\title{Introduction}

\maketitle

\phantomsection
\label{section-phantom}

This chapter contains some general information about the Clowder Project.

\ChapterTableOfContents

\section{Introduction}\label{section-introduction}
\subsection{Goals}\label{subsection-goals}
The Clowder Project has the following goals:
\begin{enumerate}
    \item\label{subsection-goals-item-1}\SloganFont{Homogenize Conventions, Notation, and Terminology. }
    \item\label{subsection-goals-item-2}\SloganFont{Fill Gaps in the Category Theory Literature. }There are quite a few significant gaps in the category theory literature, and we hope to fill some of them with the Clowder Project. For a list of some of them, see \cref{subsection-list-of-gaps-in-the-category-theory-literature}.
\end{enumerate}
\subsection{Prerequisites/Assumed Background}\label{subsection-prerequisites-assumed-background}
\subsection{Content and Scope}\label{subsection-scope}
In this section, we outline what content is expected to be covered in the Clowder Project.
\subsubsection{Elementary Category Theory}\label{subsubsection-elementary-category-theory}
First and foremost, the Clowder Project aims to cover the foundations of category theory. This comprises all the usual topics treated in basic textbooks in category theory, such as \cite{categories-for-the-working-mathematician} or \cite{category-theory-in-context}, like adjunctions, co/limits, Kan extensions, co/ends, monoidal categories, etc.
\subsection{Community Engagement and Collaboration}\label{subsection-community-engagement-and-collaboration}
\section{Miscellany}\label{section-miscellany}
\subsection{Infrastructure and Technical Implementation}\label{subsection-infrastructure-and-technical-implementation}
\subsection{List of Gaps in the Category Theory Literature}\label{subsection-list-of-gaps-in-the-category-theory-literature}
The Clowder Project aims to address several significant gaps in the existing literature on category theory, as detailed below. See also \cite{MO494959}.
\begin{gap}{The Tensor Product of Presentable Categories}{gap-the-tensor-product-of-presentable-categories}%
    Even though its analogue for $\infty$-categories has for years been a widely used tool%
    %--- Begin Footnote ---%
    \footnote{%
        See \cite{MO490557}.
        \par\vspace*{\TCBBoxCorrection}
    }, %
    %---  End Footnote  ---%
    a comprehensive treatment of the tensor product of presentable categories seems to be currently missing.
\end{gap}
\begin{gap}{Explicit Descriptions of Co/Limits of Categories}{gap-explicit-descriptions-of-co-limits-of-categories}%
    An exhaustive concrete description of the various limits and colimits of categories, including 2-dimensional ones, is missing.
\end{gap}
\begin{gap}{Dinatural Transformation Co/Classifiers}{gap-dinatural-transformation-co-classifiers}%
    There seems to be no unified presentation of dinatural transformation co/classifiers in the literature. These are characterised by isomorphisms of the form
    \[
        \Nat(F,G)%
        \cong%
        \DiNat(\Gamma(F),G),%
    \]%
    and were originally studied in Dubuc--Street's paper introducing dinatural transformations, \cite{dubuc-street-dinatural-transformations}.

    \indent Even though these arguably form a fundamental piece of the framework of co/end calculus, it seems that all foundational treatments that followed after ended up not covering this concept.
\end{gap}
\begin{gap}{The Tensor Product of Symmetric Monoidal Categories}{gap-the-tensor-product-of-symmetric-monoidal-categories}%
    The tensor product of symmetric monoidal categories had been a missing concept from the literature for years. Recently, \cite{the-symmetric-monoidal-2-category-of-permutative-categories} covered the case of permutative categories. It would be nice, however, to also have a treatment of the non-strict case available.
\end{gap}
\begin{gap}{A Comprehensive Treatment of the Theory of Promonoidal Categories}{gap-a-comprehensive-treatment-of-the-theory-of-promonoidal-categories}%
    A comprehensive and exhaustive treatment of the theory of promonoidal categories is currently missing. There are several important notions undefined, like:
    \begin{itemize}
        \item Promonoidal profunctors.
        \item Dualisability internal to a promonoidal category.
        \item Invertibility internal to a promonoidal category.
    \end{itemize}
    Moreover, it would be nice to record how promonoidal categories may be viewed as categorifications of \say{hypermonoids} (i.e.\ monoids in $\Rel$).
\end{gap}
\begin{gap}{A Comprehensive Treatment of the Theory of Multicategories}{gap-a-comprehensive-treatment-of-the-theory-of-multicategories}%
    A comprehensive and exhaustive treatment of the theory of multicategories is currently missing. There are several important notions undefined, like:
    \begin{itemize}
        \item Co/limits internal to multicategories.
    \end{itemize}
    See \cite{MO484647}.
\end{gap}
\begin{gap}{A Compendium of Examples of 2-Categorical Notions}{gap-a-compendium-of-examples-of-2-categorical-notions}%
    It would be nice to have an extensive collection of examples of what a given 2-categorical notion looks like in a 2-category. For instance, it would be nice to explicitly list what internal adjunctions look like in $\sfbfRel$, $\Span$, $\Prof$, etc.

    \indent See \ChapterRef{\ChapterRelations, \cref{relations:section-properties-of-the-2-category-of-relations}}{\cref{section-properties-of-the-2-category-of-relations}} for a concrete example of what is meant by this gap.
\end{gap}
\begin{gap}{Centres and Traces of Categories}{gap-centres-and-traces-of-categories}%
    The literature on centres and traces of categories is really small. There are lots of results missing%
    %--- Begin Footnote ---%
    \footnote{%
        E.g.\ There's a certain interaction between traces of categories and Leinster's eventual image.
    } %
    %---  End Footnote  ---%
    and very few worked examples%
    %--- Begin Footnote ---%
    \footnote{%
        E.g.\ what is the trace of Connes's cycle category? Such a computation doesn't seem to be available.
        \par\vspace*{\TCBBoxCorrection}
    }.%
    %---  End Footnote  ---%
\end{gap}
\begin{gap}{Natural Cotransformations}{gap-natural-cotransformations}%
    Natural transformations satisfy an isomorphism of the form
    \[
        \Nat(F,G)%
        \cong%
        \int_{A\in\CatFont{C}}\Hom_{\CatFont{D}}(F_{A},G_{A}).%
    \]%
    It is then exceedingly natural to define \textit{natural cotransformations} via an isomorphism of the form
    \[
        \CoNat(F,G)%
        \cong%
        \int^{A\in\CatFont{C}}\Hom_{\CatFont{D}}(F_{A},G_{A})%
    \]%
    and study their properties. This generalises traces of categories, since we have
    \[
        \Tr(\CatFont{C})%
        =%
        \CoNat(\id_{\CatFont{C}},\id_{\CatFont{C}}),
    \]%
    much like $\rmZ(\CatFont{C})=\Nat(\id_{\CatFont{C}},\id_{\CatFont{C}})$.
\end{gap}
\begin{gap}{Isbell Duality}{gap-isbell-duality}%
    There are several results and examples in the theory of Isbell duality missing from the literature, with a comprehensive treatment still lacking.
\end{gap}
\begin{gap}{A Comprehensive Theory of 2-Dimensional Co/Ends}{gap-a-comprehensive-theory-of-2-dimensional-co-ends}%
    The currently available treatments of 2-dimensional co/ends are unsatisfactory.%
    %--- Begin Footnote ---%
    \footnote{%
        For instance, none of them define 2-dimensional co/ends via 2-dimensional dinatural transformations and then go on to develop a general theory from there.
        \par\vspace*{\TCBBoxCorrection}
    }%
    %---  End Footnote  ---%
\end{gap}
\begin{gap}{A Comprehensive treatment of Factorisation Systems}{gap-a-comprehensive-treatment-of-factorisation-systems}%
    A comprehensive treatment of factorisation systems is currently missing; see \cite{MO495003}.
\end{gap}
\begin{appendices}
\input{ABSOLUTEPATH/chapters2.tex}
\end{appendices}
\end{document}
